\section{SMG Maintenance}


\subsection{Dependencies}
\subsubsection{Python}

SMG itself is written in Python code and therefore the system must
have Python available.  The initial version of Python used for SMG
development was 1.5.2.  Subsequent versions were maintained using
Python 2.2; SMG should still run under Python 1.5.2 although this has
not been specifically verified.

Python is available from:
\href{http://www.python.org/}{http://www.python.org/}.



\hypertarget{GraphViz}{\subsubsection{GraphViz}}

The GraphViz utility has been developed by AT\&T Research and converts
a text description of a graph into a representational Postscript
figure.  It can alternatively produce GIF, MIF or Web imap figures as
well.  The graphical output is very helpful in analyzing the resulting state
machine.

SMG outputs a description of the state machine itself to a \file{.dot}
file, which is then passed to GraphViz to generate the desired
graphical output. The \file{.dot} file itself is not intended for
analysis.

The GraphViz distribution version used for SMG development was 1.5.
The GraphViz package is available at:
\href{http://www.research.att.com/sw/tools/graphviz}{http://www.research.att.com/sw/tools/graphviz}


\hypertarget{Spin}{\subsubsection{Spin}}

Promela and the Spin utility are independently developed by AT\&T and
are not related to the SMG preprocessor.  Spin is available at:
\href{http://netlib.bell-labs.com/netlib/spin/whatispin.html}{http://netlib.bell-labs.com/netlib/spin/whatispin.html}


\subsubsection{Interactions}

The SMG preprocessor is an independently developed utility and is not
related to the GraphViz program developed by AT\&T nor the Python
language and interpreter developed by Guido van Rossum.  Python is
available from the above Web site.  The GraphViz program is available
independently from AT\&T under their license.


\subsection{SMG License}

Copyright (c) 2000-2003, Kevin Quick
All rights reserved.

Redistribution and use in source and binary forms, with or without
modification, are permitted provided that the conditions are met:

\begin{itemize}

\item Redistributions of source code must retain the above copyright
  notice, this list of conditions, and the following disclaimer.

\item Redistributions in binary form must reproduce the above copyright
  notice, this list of conditions and the following disclaimers in the
  documentation and/or other materials provided with the distribution.

\item Neither the name of Kevin Quick nor the names of other contributors may
  be used to endorse or promote products derived from this software
  without specific prior written permission.

\end{itemize}

THIS SOFTWARE IS PROVIDED BY THE COPYRIGHT HOLDERS AND CONTRIBUTORS
"AS IS," AND ANY EXPRESS OR IMPLIED WARRANTIES, INCLUDING, BUT NOT
LIMITED TO, THE IMPLIED WARRANTIES OF MERCHANTABILITY AND FITNESS FOR
A PARTICULAR PURPOSE ARE DISCLAIMED.  IN NO EVENT SHALL THE COPYRIGHT
HOLDERS OR ANY CONTRIBUTORS BE LIABLE FOR ANY DIRECT, INDIRECT,
INCIDENTAL, SPECIAL, EXEMPLARY, OR CONSEQUENTIAL DAMAGES (INCLUDING,
BUT NOT LIMITED TO, PROCUREMENT OF SUBSTITUTE GOODS OR SERVICES; LOSS
OF USE, DATA, OR PROFITS; OR BUSINESS INTERRUPTION) HOWEVER CAUSED AND
ON ANY THEORY OF LIABILITY, WHETHER IN CONTRACT, STRICT LIABILITY, OR
TORT (INCLUDING NEGLIGENCE OR OTHERWISE) ARISING IN ANY WAY OUT OF THE
USE OF THIS SOFTWARE, EVEN IF ADVISED OF THE POSSIBILITY OF SUCH
DAMAGE.


\subsection{SMG Change Log}

\begin{description}

\item[v1.7.2]
  \begin{itemize}
    \item Added the \code{-E} flag for generating embeddable code.
    \item Added Examples: \code{button}, \code{button2},
      \code{buttonlib} (thanks to Bob Paddock,
      \code{<bpaddock@csonline.net>})
  \end{itemize}
\item[v1.7.1]
  \begin{itemize}
  \item {\it [Internal]} Created graphviz module and modified
    \file{smg_figure} to use it.
  \end{itemize}
\item[v1.7]
  \begin{itemize}
    \item Added documentation for \SMELSE (not new to SMG, just not doc'd).
    \item Added path search for \SMINCL
    \item Added optional version parameter for \SMINCL
    \item $[$Documentation:$]$
      \begin{itemize}
      \item Document updates: clarification on \smg{<xxx>} keyword validity.
      \item Cleanup of existing examples
      \end{itemize}
    \item $[$Documentation:$]$
      \begin{itemize}
      \item Documented SMG Libraries
      \item Documented Support and Tracing Functions
      \item Documentation rearranged somewhat
      \end{itemize}
  \end{itemize}

\item[v1.6]
  \begin{itemize}
  \item Minor updates.  Preparation for SF file release.
  \item Addition of \smg{SMG_SYNTAX_A} syntax version context definition.
  \end{itemize}
  
\item[v1.5]
  \begin{itemize}
  \item Added \file{sm-mode.el} for Emacs syntax highlighting and
    indenting controls.
  \item Added handling for cascaded sub-events.
  \item Added validation to detect terminal states, source states, and
    erroneous combinations: non-\INITSTATE source states, and
    orphan states (no entries or exits)
  \item Added \code{-b} flag for bounds checking incoming events.
    This also changed the values (and ordering) for states and events
    in the \file{smdefs.h} file.
  \end{itemize}
  
\item[v1.4]
  \begin{itemize}
  \item Added the \INITSTATE for instantiation-initialized state
    machines.
  \item Modified state machine diagrams for visual identification of
    key states (initial states, final states, and the undefined
    transition error state).
  \item Expanded examples to: \file{file_ex1}, \file{file_ex2},
    \file{file_ex3}, and \file{file_ex4}.
  \end{itemize}
  
\item[v1.3]
  \begin{itemize}
  \item Added \PROMELAbegin and \PROMELAend and output of Promela code
    for spin verification.
  \item Updated \code{xx_State_Machine_Error} function to include the
    \code{err_id} for identifying and processing specific error
    numbers.
  \end{itemize}
  
\item[v1.2]
  \begin{itemize}
  \item Added clustering of nodes in figures
  \end{itemize}
  
\item[v1.1]
  \begin{itemize}
  \item Added \SMDEF, \SMIF, and \SMEND statements for conditional
    inclusion.
  \item Internal code cleanup primarily focused on:
  \item Significant Postscript output cleanup and labelling.
  \end{itemize}
  
\item[v1.0.2]
  \begin{itemize}
  \item Better tracking of source \file{.sm} file, especially for
    \SM{INCL} directives
  \item Switch to ``\code{_/}'' instead of ``\incode{_#}'' as the SMG
    identification prefix.  Still recognize the old, but the new one
    prevents macro argument replacement errors.
  \item Updated \SMTRACE for explicit macros for each type of trace
  \end{itemize}
  
\item[v1.0.1]
  \begin{itemize}
  \item Added \SMTRACE and ``\code{-T}'' command line option
    (tracing)
  \item Added ``\code{-l}'' command line option (\#line output
    suppression)
  \item Added version number and output version on help line
  \item Added \incode{_#SM_NAME} code keyword
  \item Added internal event generation deferral for
    \incode{_#<EVENT>}
  \end{itemize}
  
\end{description}

%%% Local Variables: 
%%% mode: latex
%%% TeX-master: "smg_guide"
%%% End: 
