\documentclass[runningheads]{llncs}
\usepackage{float}
\usepackage{xspace}
\usepackage[rdkeywords]{listings}
\usepackage{longtable}
\usepackage{hyperref}

\newif\ifpdf
\ifx\pdfoutput\undefined
\pdffalse    % we are not running PDFLaTeX
\else
\pdfoutput=1    % we are running PDFLaTeX
\pdftrue
\fi

\ifpdf
\usepackage[pdftex]{graphicx}
\pdfcompresslevel=9
\else
\usepackage{graphicx}
\fi

\lstloadlanguages{C}
\lstset{language=C,basicstyle=\small,commentstyle=\itshape\footnotesize,texcl=true}

\title{SMG - State Machine Generator}
\titlerunning{SMG}
\author{Kevin Quick\inst{1}}
\institute{\email{quick@null.net}}
\authorrunning{Quick}
\date{Version 1.7 \\ 16 Apr 2002}
\begin{document}
\maketitle
\input{smg_maindesc}
\input{smg_kw_brief}
\input{smg_lib}
\input{smg_lib_example}


\section{Dependencies}

SMG is written in the Python language.  It generates output that may
be passed to the AT\&T GraphViz utility for visualization and Promela
output that may be passed to the AT\&T SPIN utility.  The SMG utility
was independently developed and is not related to either the GraphViz
utility or the SPIN utility; GraphViz and SPIN they were developed
separately and may be obtained under their corresponding licenses at
\code{http://www.research.att.com/sw/tools/graphviz} and
\code{http://netlib.bell-labs.com/netlib/spin/whatispin.html},
respectively.

\section{Conclusions and Future Directions}

The SMG utility has proven to be a simple and powerful tool that can
be used to develop more maintainable and readable code, while
simultaneously supporting concurrent functional verification using
SPIN.  However, use of this tool has revealed some changes that would
increase its utility:

\begin{enumerate}
\item Simpler template for common usage.  The current minimum template
  required for SMG usage requires definitions of error functions,
  \SMOBJ and \SMEVT structure types, and proper include sequencing.
  \begin{itemize}
  \item Default object and event types could be generated, enabling
    the generation of a default error function as well to accelerate
    the generation of SMG input.
  \item Alternatively, SMG could have a ``template generation'' mode
    (specified by a command argument) that generates a standard
    minimum template automatically that can be quickly adapted to the
    specific needs of the developer.
  \end{itemize}
  
\item Control flow management.  SMG was initially designed to handle
  the delivery of external events to a state machine, and with the
  assumption that any event could occur at any point in the lifetime
  of that state machine.  However, usage has indicated that it is
  useful to correlate certain internal control flow operations to
  events.  For example, a synchronous/blocking routine often returns
  an indication of success or failure, and the state machine should
  either progress to the next normal state in the former case or enter
  an error state in the latter case.  It is possible to define events
  that correspond to these return values and to generate these events
  from within the code, but doing so is somewhat awkward---worse these
  local return values become translated into global events that SMG
  considers for {\em every} state defined.  A better method of
  handling these localized events should be identified.
  
\item Handling of synchronous/blocking functions.  SMG was developed
  primarily to handle an asynchronous non-blocking environment, and
  the directives handle this environment very naturally.  However, the
  prevalence of synchronous/blocking operations defined in POSIX
  indicates that SMG should be capable of handling these situations
  just as gracefully.  This issue is related to the Control flow
  management item above, but there may be additional adjustments
  needed for correct handling of blocking functions beyond just the
  control flow events based on the function's return value.
  
\item Generate output for other languages.  The current SMG
  implementation is only capable of generating ANSI C output for
  implementing state machines.  To increase the usefulness of the
  utility, other languages should be addressed, with the possibility
  of allowing language definition files that can be added by end-users
  without modifying core SMG code.  Potential languages include: Java,
  Python, and Perl, as well as many others.

\end{enumerate}

Despite the above issues, however, the SMG utility is a very useable
tool and further development and use of the tool is warranted.

\end{document}

